Social Participation Ontology: community documentation, enhancements and use examples

### 2015-09-18 plosOne/plos.tex
arrumacao primeira dos referenciamentos

%% END MACROS SECTION
\usepackage{xr}
\externaldocument{SI/S3original}
\externaldocument{SI/S4consultation}
\usepackage[section] {placeins}

@@

\begin{itemize}
    \item Various proposals for the \vcps\ logo, some of which are in Figure~\ref{logo}.
%    \item Figure~\ref{fig:v1} shows an English and completed version of the original diagram of \ops\ in the document~\cite{conceptualMod}. For completeness of exposition, the original diagram is Supporting Information Figure~\ref{fig:diaorig}.
    \item A diagram for general public consultations. Given the details and the pertinence of public consultations for \ops, the digram is exposed in Supporting Information Figure~\ref{fig:consult}.
\end{itemize}

@@

\begin{figure*}
    \centering
%    \includegraphics[width=\textwidth]{figs/opsTax}
    \caption{A taxonomic tree of the Ontology of Social Participation (\ops). This image was rendered inside \protege, with the \owl\ code in Appendix~\ref{owl:vcps}. Figure~\ref{fig:v1} is more informative, but this diagram is more standard and might be simpler for the newcomer. Note that the taxonomic tree does not present any information about properties further linking these classes. The prefixes {\tt snap:} and {\tt span:} are \bfo\ specific for {\tt snap}shot and {\tt span}ning-time.}
    \label{fig:owlCC}
\end{figure*}

>>>>

%% END MACROS SECTION
\usepackage{xr}
\externaldocument{SI/S2ops}
\externaldocument{SI/S3original}
\externaldocument{SI/S4consultation}
\usepackage[section] {placeins}

@@

\begin{itemize}
    \item Various proposals for the \vcps\ logo, some of which are in Figure~\ref{logo}.
    \item Figure~\ref{fig:v1} shows an English and completed version of the original diagram of \ops\ in the document~\cite{conceptualMod}. For completeness of exposition, the original diagram is Supporting Information Figure~\ref{fig:diaorig}.
    \item A diagram for general public consultations. Given the details and the pertinence of public consultations for \ops, the digram is exposed in Supporting Information Figure~\ref{fig:consult}.
\end{itemize}

@@

\begin{figure*}
    \centering
%    \includegraphics[width=\textwidth]{figs/opsTax}
    \caption{A taxonomic tree of the Ontology of Social Participation (\ops). This image was rendered inside \protege, with the \owl\ code in Supporting Information Listing~\ref{lst:ops}. Figure~\ref{fig:v1} is more informative, but this diagram is more standard and might be simpler for the newcomer. Note that the taxonomic tree does not present any information about properties further linking these classes. The prefixes {\tt snap:} and {\tt span:} are \bfo\ specific for {\tt snap}shot and {\tt span}ning-time.}
    \label{fig:owlCC}
\end{figure*}
